### 2020-12-17 paper/localpsf.tex
editing weighting functions section to be infinite dimensional

\begin{prop}
	\label{prop:equivalent_writing_of_weighting_optimization}
	Let $f \in \mathbb{R}^r$ be arbitrary. The optimization problem
	\begin{equation*}
	\begin{aligned}
	\min_{u \in H^2(\Omega)} &\quad \frac{1}{2}\norm{\Delta u}_{L^2(\Omega)}^2 \\
	\text{such that} &\quad u(x_i) = f_i, \quad i=1,\dots,r
	\end{aligned}
	\end{equation*}
	may be rewritten as follows:
	\begin{equation}
		\label{eq:generic_optimization}
		\begin{aligned}
		\min_{u \in H^2(\Omega)} &\quad \frac{1}{2} \left(\mathcal{K}\mathcal{M}^{-1}\mathcal{K}u\right)(u) \\
		\text{such that} &\quad 
		\mathcal{P} u = f.
		\end{aligned}
	\end{equation}
\end{prop}

@@

\begin{proof}
	By linearity of $\mathcal{T}$ (Corollary \ref{cor:linearity_of_solution_operator}), we have
	\begin{equation*}
		\sum_{i=1}^r w_i(x) = \sum_{i=1}^r \mathcal{T}(e_i)(x) = \mathcal{T}\left(\sum_{i=1}^r e_i\right)(x) = \mathcal{T}(\mathbf{1})(x) = 1,
	\end{equation*}
	where $\mathbf{1} = (1,1,\dots,1)$ is the length $r$ vector which has all components equal to one. The last equality, $\mathcal{T}(\mathbf{1})(x) = 1$, holds because the constant function $C \in H^2(\Omega)$, $C(x)=1$, satisfies the constraint $C(x_i) = 1$ for all $x_i$, $i=1,\dots,r$, and yields the minimum possible value of zero for the objective function, $\frac{1}{2}\|\Delta C\|^2 = 0$.
\end{proof}

>>>>

\begin{prop}
	\label{prop:equivalent_writing_of_weighting_optimization}
	Let $f \in \mathbb{R}^r$ be arbitrary. The optimization problem
	\begin{equation}
	\label{eq:generic_optimization_initial}
	\begin{aligned}
	\min_{u \in H^2(\Omega)} &\quad \frac{1}{2}\norm{\Delta u}_{L^2(\Omega)}^2 \\
	\text{such that} &\quad u(x_i) = f_i, \quad i=1,\dots,r
	\end{aligned}
	\end{equation}
	may be rewritten as follows:
	\begin{equation}
		\label{eq:generic_optimization}
		\begin{aligned}
		\min_{u \in H^2(\Omega)} &\quad \frac{1}{2} \left(\mathcal{K}\mathcal{M}^{-1}\mathcal{K}u\right)(u) \\
		\text{such that} &\quad 
		\mathcal{P} u = f.
		\end{aligned}
	\end{equation}
\end{prop}

@@

\begin{proof}
	By linearity of $\mathcal{T}$ (Corollary \ref{cor:linearity_of_solution_operator}), we have
	\begin{equation*}
		\sum_{i=1}^r w_i(x) = \sum_{i=1}^r \mathcal{T}(e_i)(x) = \mathcal{T}\left(\sum_{i=1}^r e_i\right)(x) = \mathcal{T}(\mathbf{1})(x) = 1,
	\end{equation*}
	where $\mathbf{1} = (1,1,\dots,1)$ is the length $r$ vector which has all components equal to one. The last equality ($\mathcal{T}(\mathbf{1})(x) = 1$) holds because the constant function $C \in H^2(\Omega)$, $C(x)=1$, satisfies the constraint of optimization problem \eqref{eq:generic_optimization_initial} with $f = \mathbf{1}$, and yields the minimum possible value of zero for the objective function (i.e., $C(x_i) = 1$ for $i=1,\dots,r$,  and $\frac{1}{2}\|\Delta C\|^2 = 0$).
\end{proof}
